Using traffic analysis to identify The Second Generation Onion Router

### 2011-01-30 thesis/thesis.tex
3-4 instead of 'p. 3-4' uses appropriate pages label

Tor was first described in \citetitle{Dingledine:2004p314}
\parencite{Dingledine:2004p314}. This new generation of onion router was
designed with a number of defences for common traffic analysis attacks and
weaknesses discovered in other proposals. With a focus on deployability,
usability, flexibility and simple-design \parencite[p. 3-4]{Dingledine:2004p314}
as well as a successful implementation, it has seen wider deployment than most
other anonymous networks.

>>>>

Tor was first described in \citetitle{Dingledine:2004p314}
\parencite{Dingledine:2004p314}. This new generation of onion router was
designed with a number of defences for common traffic analysis attacks and
weaknesses discovered in other proposals. With a focus on deployability,
usability, flexibility and simple-design \parencite[3-4]{Dingledine:2004p314}
as well as a successful implementation, it has seen wider deployment than most
other anonymous networks.
